Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
temp push to sync

@@

Then, the runtime of Parareal is, assuming negligible setup and
aggregation time,

@@

The first t seconds comes from the first coarse approximation, without which the parareal algorithm degenerates to $g_{\Delta t}$. In order for there to be a speedup relative to the fine operator, we require
that $t + k(t + Qt/N) < Qt$, or $k < \frac{Q - 1}{1 + Q/N}$ or $N > \frac{Qk}{Q
- 1 - k}$. This can be tuned with by either adjusting the the quality factor or reducing the number of iterations, but the number of iterations, k, is important for error convergence to that of $g_{\textnormal{fine}}$. However, this optimal k is a problem-specific parameter and must be optimized for.

TODO PARALLEL IN SPACE ANALYSIS

@@

TODO PARALLEL IN SPACE ANALYSIS

>>>>

\subsubsection{Parareal}

@@

Then, the runtime of Parareal is, assuming negligible overhead and ignoring communication speeds and letting $t$ be the time in seconds to compute the coarse $g_{\Delta t}$:

@@

The first $t$ seconds comes from the first coarse approximation, without which the parareal algorithm degenerates to $g_{\Delta t}$.  Then for each of the $k$ correction iterations, the $t$ term comes from $n$, element by element evaluations of  $g_{\Delta t}$ followed by a parallel $\frac{1}{N}$ evaluation of $g_{\textnormal{fine}}$. In order for there to be a speedup relative to the fine operator, we can rearrange to get:

\begin{equation}
\begin{aligned}
t + k\left( t + \frac{Qt}{N} \right) &< Qt \\
k &< \frac{Q - 1}{1 + Q/N} \\
N &> \frac{Qk}{Q - 1 - k} \\
\end{aligned}
\end{equation}

This can be tuned with by either adjusting the the quality factor or reducing the number of iterations, but the number of iterations, $k$, is important for error convergence to that of $g_{\textnormal{fine}}$.  However, finding the optimal $k$ is a problem-specific parameter and traded off for the desired accepted error.

\subsubsection{Parallel By Space}

@@

\subsubsection{Parareal}

\subsubsection{Parallel By Space}
